Evaluate PEER in each cohort and brain region

### 2021-02-18 combined_analysis/eval_resid_in_each.Rmd
add more summary info

METADATA %>% group_by(Cohort, Region) %>% dplyr::summarise(count = n()) %>%  kable(caption="Cohort, Region") %>% kable_styling(full_width=FALSE) 
```

>>>>

METADATA %>% group_by(Cohort, Region) %>% dplyr::summarise(count = n()) %>%  kable(caption="Cohort, Region") %>% kable_styling(full_width=FALSE)

METADATA %>% group_by(Cohort, Region, Ethnicity) %>% dplyr::summarise(count = n()) %>%  kable(caption="Cohort, Region") %>% kable_styling(full_width=FALSE) 
```
